---
title: "Besler_Jan_AssignmentV"
author: "Jan Besler"
date: "13/02/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/home/jan/Uni/Data_Science/Project_Management/Assignments_DSPM/")
knitr::opts_chunk$set(echo = TRUE)
```

### Setup
Before starting workspace is cleared and all necessary libraries are loaded.
```{r libraries, echo=TRUE, message=FALSE, warning=FALSE}
# clear workspace
rm(list = ls())

# load libraries
library(maps)
library(ggplot2)
library(tidyr)
library(plyr)
library(dplyr)
library(jsonlite)
library(httr)
library(rlist)
```

# Exercise 1: Setting up a new GitHub repository

>**1.1** Register on github.com in case you have not done this already.

>**1.2** Initialize a new public repository for this assignment on GitHub.

The linked repository can be found at:
https://github.com/janbesler/Assignment_V_GitHub

# Exercise 2: Getting to know the API

>**2.1** Visit the documentation website for the API provided by ticketmaster.com

>**2.2** Familiarize yourself with the features and functionalities of the Ticketmaster Discovery API. Have a particular look at rate limits.

First we look at the documentation of the Ticketmaster API (https://developer.ticketmaster.com/products-and-docs/apis/getting-started/) to get the necessary information on how the database is structured and what the "rules" are, e.g. rate limits and ToS.
The rate limit shown on the page lies at 5000 calls per day as of 31/01/2021.

>**2.3** Whithin the scope of this assignment, you do not have to request your own API key. Instead retrieve
a valid key from the API Explorer. This API key enables you to perform the GET requests needed
throughout this assignment.

The API key is a publicly available on the API Explorer (https://developer.ticketmaster.com/api-explorer/v2/).

>**2.4** Even though this API key is not secret per se (it is publicly visible onn the API Explorer website),
please comply to the common secrecy practices discussed in the lecture and the tutorial: Treat the API
key as a secret token. Your API key should neither appear in the code that you are submitting nor in
your public GitHub repository.

```{r api}
A5_key <- source("~/Uni/Data_Science/Project_Management/Assignments_DSPM/api-key.R")

```

The key is stored separately on a file on a local machine.

## basic API Interaction
In the first step the results from the first site are printed and are compiled into a data frame.
The output looks like this:

``` {r api_basic}
res_venue <- GET(url  = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "DE"))
content_venue_DE <- jsonlite::fromJSON(content(res_venue, as = "text"))
df_venue_DE <- data.frame(content_venue_DE$'_embedded'$venues)

```

If we use the content function on the venue data for Germany we get a list of 19 Variables. But some of the required information is stored in a data frame itself inside the first data frame. This applies for the city-, address- and location-variable.

``` {r api_basic_slicing}
df_venue_basic <- data.frame(
            name = df_venue_DE$name,
            city = df_venue_DE$city$name,
            postalCode = df_venue_DE$postalCode,
            address = df_venue_DE$address$line1,
            url = df_venue_DE$url,
            longitude = df_venue_DE$location$longitude,
            latitude = df_venue_DE$location$latitude
        )
glimpse(df_venue_basic)
```
Now the first 20 values are in the desired standard data frame format.

## API advanced

Since the first basic step only shows the results for the first 20 results, hence the first site. The following part is resolving this problem by iterating the pagenumbers until there are less than 20 values on a page.

From this point onwards only code is shown withou its results, because there is an error on my API request and markdown won't knit the document if don't set eval to false for those chunks. As a result it can't process the required data frames in order to plot the maps.

``` {r api_advanced, eval = FALSE}

info_DE <- content(GET(url  = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "DE",
                                 size = 50)))
pages_DE <- info_DE$page$totalPages
N_DE <- round_any(info_DE$page$totalElements, 50, floor)

df_venue_advanced <- data.frame(
            name = character(N_DE),
            city = character(N_DE),
            postalCode = numeric(N_DE),
            address = character(N_DE),
            url = character(N_DE),
            longitude = numeric(N_DE),
            latitude = numeric(N_DE),
            stringsAsFactors = FALSE
            )

for (i in 1:(pages_DE + 1)) {
  iterated_results_DE <- GET(url  = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "DE",
                                 size = 50,
                                 page = i-1))

  iterated_venue_DE <- jsonlite::fromJSON(content(iterated_results_DE, as = "text"))[['_embedded']][['venues']]

  df_venue_advanced[((i-1)*50+1):(i*50),] <- data.frame(
                                           iterated_venue_DE$name,
                                           iterated_venue_DE$city$name,
                                           iterated_venue_DE$postalCode,
                                           iterated_venue_DE$address$line1,
                                           iterated_venue_DE$url,
                                           as.double(iterated_venue_DE$location$longitude),
                                           as.double(iterated_venue_DE$location$latitude)
                                           )
  Sys.sleep(2)
}

df_venue_advanced <- df_venue_advanced[df_venue_advanced$postalCode != 0,]

```
#### acknowledging my ignorance 

for some reason I don't fully understand my code stops working with the second last line.
However it works somehow for the first 200 values until the error "arguments imply differing number of rows: 50, 0" appears, which I assume has something to do with the last page and the less than 50 values on it. I tried to fix this by rounding the number down to a number which can be divided by 50, but this didn't seemed to do the trick.
But even if it shows an error message, the first 200 results are still processed, these can be used in the next step, the creation of a map. Therefor I leave it as it is.

## event locations

With the flawed data frame the map is going to be flawed to. But here I encountered another value I don't fully understand.
I tried to drop all values with a postalCode of 0, to get rid of the faulty values in my data frame, yet one value simply doesn't drop and I again don't know why. The line 202 shows an empty row with the value 0 for the postalCode and values of 0 for the coordinates. Hence if the map is plotted it is rather small with one point ath the crosssection of the equator and the prime meridian.

``` {r DE_plot, eval = FALSE}
map_DE <- na.omit(df_venue_advanced)
map_DE <- map_DE[!(df_venue_advanced$longitude < "5.866944"),] 
map_DE <- map_DE[!(df_venue_advanced$longitude > "15.043611"),] 
map_DE <- map_DE[!(df_venue_advanced$latitude < "47.271679"),]
map_DE <- map_DE[!(df_venue_advanced$latitude > "55.0846"),]
map_DE <- map_DE[df_venue_advanced$longitude != 0,]

ger_venue <- ggplot() +
  geom_polygon(
  aes(x = long, y = lat, group = group), data = map_data("world", region = "Germany"),
  fill = "grey90",color = "black") +
  theme_void() + coord_quickmap() +
  labs(title = "Event locations across Germany", caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
  plot.caption = element_text(face = "italic")) +
  geom_point(data = map_DE, aes(x = longitude, y = latitude), na.rm = TRUE)
ger_venue
 
```

## API other countries

The same code was applied to 3 different countries in Europe. Sweden, Italy and Belgium.
The results are then processed in the same graphical manner as the results for Germany previously.
Since the same code is used, the same errors emerge.

``` {r countries_belgium, eval = FALSE}

info_BE <- content(GET(url  = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "BE",
                                 size = 50)))
pages_BE <- info_BE$page$totalPages
N_BE <- round_any(info_BE$page$totalElements, 50, floor) #gives the required solution from the Assignment

df_venue_BE <- data.frame(
            name = character(N_BE),
            city = character(N_BE),
            postalCode = numeric(N_BE),
            address = character(N_BE),
            url = character(N_BE),
            longitude = numeric(N_BE),
            latitude = numeric(N_BE),
            stringsAsFactors = FALSE
            )

for (i in 1:(N_BE+1)) {
  iterated_results_BE <- GET(url  = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "BE",
                                 size = 50,
                                 page = i-1))

  iterated_venue_BE <- jsonlite::fromJSON(content(iterated_results_BE, as = "text"))[['_embedded']][['venues']]

  df_venue_BE[((i-1)*50+1):(i*50),] <- data.frame(
                                           iterated_venue_BE$name,
                                           iterated_venue_BE$city$name,
                                           iterated_venue_BE$postalCode,
                                           iterated_venue_BE$address$line1,
                                           iterated_venue_BE$url,
                                           as.double(iterated_venue_BE$location$longitude),
                                           as.double(iterated_venue_BE$location$latitude)
                                           )
  Sys.sleep(0.75)
}

df_venue_BE <- df_venue_BE[df_venue_BE$postalCode != 0,]
```

``` {r countries_sweden, eval = FALSE}
info_SE <- content(GET(url  = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "SE",
                                 size = 50)))
pages_SE <- info_SE$page$totalPages
N_SE <- round_any(info_SE$page$totalElements, 50, floor) #gives the required solution from the Assignment

df_venue_SE <- data.frame(
            name = character(N_SE),
            city = character(N_SE),
            postalCode = numeric(N_SE),
            address = character(N_SE),
            url = character(N_SE),
            longitude = numeric(N_SE),
            latitude = numeric(N_SE),
            stringsAsFactors = FALSE
            )

for (i in 1:(N_SE+1)) {
  iterated_results_SE <- GET(url  = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "SE",
                                 size = 50,
                                 page = i-1))

  iterated_venue_SE <- jsonlite::fromJSON(content(iterated_results_SE, as = "text"))[['_embedded']][['venues']]

  df_venue_SE[((i-1)*50+1):(i*50),] <- data.frame(
                                           iterated_venue_SE$name,
                                           iterated_venue_SE$city$name,
                                           iterated_venue_SE$postalCode,
                                           iterated_venue_SE$address$line1,
                                           iterated_venue_SE$url,
                                           as.double(iterated_venue_SE$location$longitude),
                                           as.double(iterated_venue_SE$location$latitude)
                                           )
  Sys.sleep(0.75)
}

df_venue_SE <- df_venue_SE[df_venue_SE$postalCode != 0,]
```

#### uniqueness of sweden
This chunk is interesting since it never finishes its iteration and had to be manually stopped, to get any result to work with for the map.

``` {r countries_italy, eval = FALSE}
info_IT <- content(GET(url  = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "IT",
                                 size = 50)))
pages_IT <- info_IT$page$totalPages
N_IT <- round_any(info_IT$page$totalElements, 50, floor) #gives the required solution from the Assignment

df_venue_IT <- data.frame(
            name = character(N_IT),
            city = character(N_IT),
            postalCode = numeric(N_IT),
            address = character(N_IT),
            url = character(N_IT),
            longitude = numeric(N_IT),
            latitude = numeric(N_IT),
            stringsAsFactors = FALSE
            )

for (i in 1:(N_IT+1)) {
  iterated_results_IT <- GET(url  = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "IT",
                                 size = 50,
                                 page = i-1))

  iterated_venue_IT <- jsonlite::fromJSON(content(iterated_results_IT, as = "text"))[['_embedded']][['venues']]

  df_venue_IT[((i-1)*50+1):(i*50),] <- data.frame(
                                           iterated_venue_IT$name,
                                           iterated_venue_IT$city$name,
                                           iterated_venue_IT$postalCode,
                                           iterated_venue_IT$address$line1,
                                           iterated_venue_IT$url,
                                           as.double(iterated_venue_IT$location$longitude),
                                           as.double(iterated_venue_IT$location$latitude)
                                           )
  Sys.sleep(0.75)
}

df_venue_IT <- df_venue_IT[df_venue_IT$postalCode != 0,] 

```



``` {r countries_maps, eval = FALSE}

map_BE <- na.omit(df_venue_BE)
map_BE <- map_BE[!(df_venue_BE$longitude < "5.866944"),] #west
map_BE <- map_BE[!(df_venue_BE$longitude > "6.23"),] #east
map_BE <- map_BE[!(df_venue_BE$latitude < "49.3"),] #south
map_BE <- map_BE[!(df_venue_BE$latitude > "51.2952"),] #north
map_BE <- na.omit(map_BE)

bel_venue <- ggplot() +
    geom_polygon(
  aes(x = long, y = lat, group = group), data = map_data("world", region = "Belgium"),
  fill = "grey90",color = "black") +
  theme_void() + coord_quickmap() +
  labs(title = "Event locations across Belgium", caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
  plot.caption = element_text(face = "italic")) +
  geom_point(data = map_BE, aes(x = longitude, y = latitude), na.rm = TRUE)
bel_venue

map_SE <- na.omit(df_venue_SE)
map_SE <- map_SE[!(df_venue_SE$longitude < "11.113"),] #west
map_SE <- map_SE[!(df_venue_SE$longitude > "24.155833"),] #east
map_SE <- map_SE[!(df_venue_SE$latitude < "55.3369"),] #south
map_SE <- map_SE[!(df_venue_SE$latitude > "69.06"),] # north
map_SE <- na.omit(df_venue_SE)

se_venue <- ggplot() +
  geom_polygon(
  aes(x = long, y = lat, group = group), data = map_data("world", region = "Sweden"),
  fill = "grey90",color = "black") +
  theme_void() + coord_quickmap() +
  labs(title = "Event locations across Sweden", caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
  plot.caption = element_text(face = "italic")) +
  geom_point(data = map_SE, aes(x = longitude, y = latitude), na.rm = TRUE)
se_venue

map_IT <- na.omit(df_venue_IT)
map_IT <- map_IT[!(df_venue_IT$longitude < "6.37"),] #west
map_IT <- map_IT[!(df_venue_IT$longitude > "18.31"),] #east
map_IT <- map_IT[!(df_venue_IT$latitude < "37.56"),] #south
map_IT <- map_IT[!(df_venue_IT$latitude > "47.5"),] #north
map_IT <- na.omit(df_venue_IT)

it_venue <- ggplot() +
  geom_polygon(
  aes(x = long, y = lat, group = group), data = map_data("world", region = "Italy"),
  fill = "grey90",color = "black") +
  theme_void() + coord_quickmap() +
  labs(title = "Event locations across Italy", caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
  plot.caption = element_text(face = "italic")) +
  geom_point(data = map_IT, aes(x = longitude, y = latitude), na.rm = TRUE)
it_venue

```
It again seems like previously, that emitting false coordinates isn't working as intended since for example row 126 in map_BE has a values outside of the perimeters declared previously to the plotting. Same result apply towards the map of Sweden.
While the map for Italy works perfectly fine.

## GitHub

I pushed my progress regularly to GitHub and tried to give it meaningful comments.
The data can be found on:
https://github.com/v0lker42/Assignment_V_GitHub