---
title: "Besler_Jan_AssignmentV"
author: "Jan Besler"
date: "13/02/2021"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/home/jan/Uni/Data_Science/Project_Management/Assignments_DSPM/")
knitr::opts_chunk$set(echo = TRUE)
```

### Setup
Before starting workspace is cleared.
```{r workspace, echo=TRUE, message=FALSE, warning=FALSE}
# clear workspace
rm(list = ls())

```

# Exercise 1: Setting up a new GitHub repository

>**1.1** Register on github.com in case you have not done this already.

>**1.2** Initialize a new public repository for this assignment on GitHub.

The linked repository can be found at:
https://github.com/janbesler/Assignment_V_GitHub

# Exercise 2: Getting to know the API

>**2.1** Visit the documentation website for the API provided by ticketmaster.com

>**2.2** Familiarize yourself with the features and functionalities of the Ticketmaster Discovery API. Have a particular look at rate limits.

First we look at the documentation of the Ticketmaster API (https://developer.ticketmaster.com/products-and-docs/apis/getting-started/) to get the necessary information on how the database is structured and what the "rules" are, e.g. rate limits and ToS.
The rate limit shown on the page lies at 5000 calls per day as of 31/01/2021.

>**2.3** Whithin the scope of this assignment, you do not have to request your own API key. Instead retrieve
a valid key from the API Explorer. This API key enables you to perform the GET requests needed
throughout this assignment.

The API key is a publicly available on the API Explorer (https://developer.ticketmaster.com/api-explorer/v2/).

>**2.4** Even though this API key is not secret per se (it is publicly visible onn the API Explorer website),
please comply to the common secrecy practices discussed in the lecture and the tutorial: Treat the API
key as a secret token. Your API key should neither appear in the code that you are submitting nor in
your public GitHub repository.

```{r api, echo=TRUE, message=FALSE, warning=FALSE}
A5_key <- source("~/Uni/Data_Science/Project_Management/Assignments_DSPM/api-key.R")

```

The key is stored separately on a file on a local machine.

# Exercise 3: Interacting with the API - the basics

>**3.1** Load the packages needed to interact with APIs using R.

``` {r libraries, echo=TRUE, message=FALSE, warning=FALSE}
# load libraries
library(maps)
library(ggplot2)
library(tidyr)
library(plyr)
library(dplyr)
library(jsonlite)
library(httr)
library(rlist)
```

>**3.2** Perform a first GET request, that searches for event venues in Germany (countryCode = "DE"). Extract
the content from the response object and inspect the resulting list. Describe what you can see.

In the first step the results from the first site are printed and are compiled into a data frame.

``` {r api_basic}
res_venue <- GET(url  = "https://app.ticketmaster.com/discovery/v2/venues/",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "DE"))
content_venue_DE <- jsonlite::fromJSON(content(res_venue, as = "text"))
df_venue_DE <- data.frame(content_venue_DE$'_embedded'$venues)

df_venue_DE
```

If we use the content function on the venue data for Germany we get a list of 19 Variables. But some of the required information is stored in a data frame itself inside the first data frame. This applies for the city-, address- and location-variable.

>**3.3** Extract the name, the city, the postalCode and address, as well as the url and the longitude and
latitude of the venues to a data frame.

``` {r api_basic_slicing}
df_venue_basic <- data.frame(
              name = event_venues_cleaned[["_embedded"]][["venues"]][["name"]],
              city = event_venues_cleaned[["_embedded"]][["venues"]][["city"]][["name"]],
              postalCode = event_venues_cleaned[["_embedded"]][["venues"]][["postalCode"]],
              address = event_venues_cleaned[["_embedded"]][["venues"]][["address"]][["line1"]],
              url = event_venues_cleaned[["_embedded"]][["venues"]][["url"]],
              longitude = event_venues_cleaned[["_embedded"]][["venues"]][["location"]][["longitude"]],
              latitude = event_venues_cleaned[["_embedded"]][["venues"]][["location"]][["latitude"]]
        )
glimpse(df_venue_basic)
```
Now the first 20 values are in the desired standard data frame format.

# Exercise 4: Interacting with the API - advanced
>**4.1** Have a closer look at the list element named page. Did your GET request from exercise 3 return all
event locations in Germany? Obviously not - there are of course much more venues in Germany than
those contained in this list. Your GET request only yielded the first results page containing the first 20
out of several thousands of venues.

>**4.2** Check the API documentation under the section Venue Search. How can you request the venues from
the remaining results pages?

The idea is to iterate the page numbers until there are less values on a page than the size of searching.

>**4.3** Write a for loop that iterates through the results pages and performs a GET request for all venues
in Germany. After each iteration, extract the seven variables name, city, postalCode, address, url,
longitude, and latitude. Join the information in one large data frame.

From this point on wards only code is shown without its results, because there is an error on my API request and markdown won't knit the document if don't set eval to false for those chunks. As a result it can't process the required data frames in order to plot the maps.

``` {r api_advanced, echo=TRUE, message=FALSE, warning=FALSE}

number_events <- content_venue_DE[[3]]$totalElements
page_size <- 100
pages_DE <- floor(number_events/page_size)  # info_DE$page$totalPages
last_page <- number_events - pages_DE * page_size

df_venue_advanced <- data.frame(
            name = character(number_events),
            city = character(number_events),
            postalCode = numeric(number_events),
            address = character(number_events),
            url = character(number_events),
            longitude = rep(NA, number_events),
            latitude = rep(NA, number_events)
            )

for (i in 1:pages_DE){
  iterated_results_DE <- GET(url  = "https://app.ticketmaster.com/discovery/v2/venues/",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "DE",
                                 size = page_size,
                                 page = (i-1)
                           )
                    )

  iterated_venue_DE <- jsonlite::fromJSON(content(iterated_results_DE, as = "text"))

  df_venue_advanced[((i-1)*50+1):(i*50),] <- data.frame(
                                           iterated_venue_DE$name,
                                           iterated_venue_DE$city$name,
                                           iterated_venue_DE$postalCode,
                                           iterated_venue_DE$address$line1,
                                           iterated_venue_DE$url,
                                           as.double(iterated_venue_DE$location$longitude),
                                           as.double(iterated_venue_DE$location$latitude)
                                           )
  Sys.sleep(2)
}

df_venue_advanced <- df_venue_advanced[df_venue_advanced$postalCode != 0,]

```


## event locations

With the flawed data frame the map is going to be flawed to. But here I encountered another value I don't fully understand.
I tried to drop all values with a postalCode of 0, to get rid of the faulty values in my data frame, yet one value simply doesn't drop and I again don't know why. The line 202 shows an empty row with the value 0 for the postalCode and values of 0 for the coordinates. Hence if the map is plotted it is rather small with one point ath the crosssection of the equator and the prime meridian.

``` {r DE_plot, eval = FALSE}
map_DE <- na.omit(df_venue_advanced)
map_DE <- map_DE[!(df_venue_advanced$longitude < "5.866944"),] 
map_DE <- map_DE[!(df_venue_advanced$longitude > "15.043611"),] 
map_DE <- map_DE[!(df_venue_advanced$latitude < "47.271679"),]
map_DE <- map_DE[!(df_venue_advanced$latitude > "55.0846"),]
map_DE <- map_DE[df_venue_advanced$longitude != 0,]

ger_venue <- ggplot() +
  geom_polygon(
  aes(x = long, y = lat, group = group), data = map_data("world", region = "Germany"),
  fill = "grey90",color = "black") +
  theme_void() + coord_quickmap() +
  labs(title = "Event locations across Germany", caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
  plot.caption = element_text(face = "italic")) +
  geom_point(data = map_DE, aes(x = longitude, y = latitude), na.rm = TRUE)
ger_venue
 
```

## API other countries

The same code was applied to 3 different countries in Europe. Sweden, Italy and Belgium.
The results are then processed in the same graphical manner as the results for Germany previously.
Since the same code is used, the same errors emerge.

``` {r countries_belgium, eval = FALSE}

info_BE <- content(GET(url  = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "BE",
                                 size = 50)))
pages_BE <- info_BE$page$totalPages
N_BE <- round_any(info_BE$page$totalElements, 50, floor) #gives the required solution from the Assignment

df_venue_BE <- data.frame(
            name = character(N_BE),
            city = character(N_BE),
            postalCode = numeric(N_BE),
            address = character(N_BE),
            url = character(N_BE),
            longitude = numeric(N_BE),
            latitude = numeric(N_BE),
            stringsAsFactors = FALSE
            )

for (i in 1:(N_BE+1)) {
  iterated_results_BE <- GET(url  = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "BE",
                                 size = 50,
                                 page = i-1))

  iterated_venue_BE <- jsonlite::fromJSON(content(iterated_results_BE, as = "text"))[['_embedded']][['venues']]

  df_venue_BE[((i-1)*50+1):(i*50),] <- data.frame(
                                           iterated_venue_BE$name,
                                           iterated_venue_BE$city$name,
                                           iterated_venue_BE$postalCode,
                                           iterated_venue_BE$address$line1,
                                           iterated_venue_BE$url,
                                           as.double(iterated_venue_BE$location$longitude),
                                           as.double(iterated_venue_BE$location$latitude)
                                           )
  Sys.sleep(0.75)
}

df_venue_BE <- df_venue_BE[df_venue_BE$postalCode != 0,]
```

``` {r countries_sweden, eval = FALSE}
info_SE <- content(GET(url  = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "SE",
                                 size = 50)))
pages_SE <- info_SE$page$totalPages
N_SE <- round_any(info_SE$page$totalElements, 50, floor) #gives the required solution from the Assignment

df_venue_SE <- data.frame(
            name = character(N_SE),
            city = character(N_SE),
            postalCode = numeric(N_SE),
            address = character(N_SE),
            url = character(N_SE),
            longitude = numeric(N_SE),
            latitude = numeric(N_SE),
            stringsAsFactors = FALSE
            )

for (i in 1:(N_SE+1)) {
  iterated_results_SE <- GET(url  = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "SE",
                                 size = 50,
                                 page = i-1))

  iterated_venue_SE <- jsonlite::fromJSON(content(iterated_results_SE, as = "text"))[['_embedded']][['venues']]

  df_venue_SE[((i-1)*50+1):(i*50),] <- data.frame(
                                           iterated_venue_SE$name,
                                           iterated_venue_SE$city$name,
                                           iterated_venue_SE$postalCode,
                                           iterated_venue_SE$address$line1,
                                           iterated_venue_SE$url,
                                           as.double(iterated_venue_SE$location$longitude),
                                           as.double(iterated_venue_SE$location$latitude)
                                           )
  Sys.sleep(0.75)
}

df_venue_SE <- df_venue_SE[df_venue_SE$postalCode != 0,]
```

#### uniqueness of sweden
This chunk is interesting since it never finishes its iteration and had to be manually stopped, to get any result to work with for the map.

``` {r countries_italy, eval = FALSE}
info_IT <- content(GET(url  = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "IT",
                                 size = 50)))
pages_IT <- info_IT$page$totalPages
N_IT <- round_any(info_IT$page$totalElements, 50, floor) #gives the required solution from the Assignment

df_venue_IT <- data.frame(
            name = character(N_IT),
            city = character(N_IT),
            postalCode = numeric(N_IT),
            address = character(N_IT),
            url = character(N_IT),
            longitude = numeric(N_IT),
            latitude = numeric(N_IT),
            stringsAsFactors = FALSE
            )

for (i in 1:(N_IT+1)) {
  iterated_results_IT <- GET(url  = "https://app.ticketmaster.com/discovery/v2/venues.json?",
                    query = list(apikey = A5_key[1],
                                 locale = "*",
                                 countryCode = "IT",
                                 size = 50,
                                 page = i-1))

  iterated_venue_IT <- jsonlite::fromJSON(content(iterated_results_IT, as = "text"))[['_embedded']][['venues']]

  df_venue_IT[((i-1)*50+1):(i*50),] <- data.frame(
                                           iterated_venue_IT$name,
                                           iterated_venue_IT$city$name,
                                           iterated_venue_IT$postalCode,
                                           iterated_venue_IT$address$line1,
                                           iterated_venue_IT$url,
                                           as.double(iterated_venue_IT$location$longitude),
                                           as.double(iterated_venue_IT$location$latitude)
                                           )
  Sys.sleep(0.75)
}

df_venue_IT <- df_venue_IT[df_venue_IT$postalCode != 0,] 

```



``` {r countries_maps, eval = FALSE}

map_BE <- na.omit(df_venue_BE)
map_BE <- map_BE[!(df_venue_BE$longitude < "5.866944"),] #west
map_BE <- map_BE[!(df_venue_BE$longitude > "6.23"),] #east
map_BE <- map_BE[!(df_venue_BE$latitude < "49.3"),] #south
map_BE <- map_BE[!(df_venue_BE$latitude > "51.2952"),] #north
map_BE <- na.omit(map_BE)

bel_venue <- ggplot() +
    geom_polygon(
  aes(x = long, y = lat, group = group), data = map_data("world", region = "Belgium"),
  fill = "grey90",color = "black") +
  theme_void() + coord_quickmap() +
  labs(title = "Event locations across Belgium", caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
  plot.caption = element_text(face = "italic")) +
  geom_point(data = map_BE, aes(x = longitude, y = latitude), na.rm = TRUE)
bel_venue

map_SE <- na.omit(df_venue_SE)
map_SE <- map_SE[!(df_venue_SE$longitude < "11.113"),] #west
map_SE <- map_SE[!(df_venue_SE$longitude > "24.155833"),] #east
map_SE <- map_SE[!(df_venue_SE$latitude < "55.3369"),] #south
map_SE <- map_SE[!(df_venue_SE$latitude > "69.06"),] # north
map_SE <- na.omit(df_venue_SE)

se_venue <- ggplot() +
  geom_polygon(
  aes(x = long, y = lat, group = group), data = map_data("world", region = "Sweden"),
  fill = "grey90",color = "black") +
  theme_void() + coord_quickmap() +
  labs(title = "Event locations across Sweden", caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
  plot.caption = element_text(face = "italic")) +
  geom_point(data = map_SE, aes(x = longitude, y = latitude), na.rm = TRUE)
se_venue

map_IT <- na.omit(df_venue_IT)
map_IT <- map_IT[!(df_venue_IT$longitude < "6.37"),] #west
map_IT <- map_IT[!(df_venue_IT$longitude > "18.31"),] #east
map_IT <- map_IT[!(df_venue_IT$latitude < "37.56"),] #south
map_IT <- map_IT[!(df_venue_IT$latitude > "47.5"),] #north
map_IT <- na.omit(df_venue_IT)

it_venue <- ggplot() +
  geom_polygon(
  aes(x = long, y = lat, group = group), data = map_data("world", region = "Italy"),
  fill = "grey90",color = "black") +
  theme_void() + coord_quickmap() +
  labs(title = "Event locations across Italy", caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
  plot.caption = element_text(face = "italic")) +
  geom_point(data = map_IT, aes(x = longitude, y = latitude), na.rm = TRUE)
it_venue

```
It again seems like previously, that emitting false coordinates isn't working as intended since for example row 126 in map_BE has a values outside of the perimeters declared previously to the plotting. Same result apply towards the map of Sweden.
While the map for Italy works perfectly fine.

## GitHub

I pushed my progress regularly to GitHub and tried to give it meaningful comments.
The data can be found on:
https://github.com/v0lker42/Assignment_V_GitHub